\cvsection{Projects}
\begin{cventries}
%   \cventry
%     {Run on MXNet in Python}
%     {Curiosity-LSTM}
%     {}
%     {Apr. 2017 - NOW}
%     {
%       \begin{cvitems}
%         \item {Define the item novelty criteria.}
%         \item {Reconstruct LSTM to fit novelty, implement the algorithm.}
%       \end{cvitems}
%     }
  \cventry
    {Run on MXNet in Python}
    {Deep Audio-based Music Recommendation}
    {}
    {Jul. 2016 - Jul. 2017}
    {
      \begin{cvitems}
        \item {Collecting MSD, Echo Nest Taste Profile, and 7 Digital Music Clips Datasets.}
        \item {Uses convolutional neural networks to analyzes audio information by extraction frame-level features.}
        \item {Improve the accuracy of the music recommendation in collaborative filtering latent space.}
      \end{cvitems}
    }
  \cventry
    {Written in Python}
    {Sogou Persona Prediction}
    {}
    {Nov. 2016}
    {
      \begin{cvitems}
        \item {Applying LDA to each user's query list to draw topic features.}
        \item {Uses SVM and a 5 layers LSTM network to produce the predictions.}
      \end{cvitems}
    }
  \cventry
    {Written in Java}
    {UIS: A novel SNS User recommendation framework}
    {}
    {Oct. 2015 - Oct. 2016}
    {
      \begin{cvitems}
        \item {Implement our improved LDA model.}
        \item {Parameter tuning and summarise experimental results.}
      \end{cvitems}
    }
  \cventry
    {Python for data crawling, mongoDB for storage, Lucene for query}
    {Gitsoo: An academic vertical searching engine}
    {}
    {Dec. 2015 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Responsible for the search, sorting algorithm development and data indexing.}
        \item {Responsible for the development of data crawling, MongoDB data storage, and backend Lucene search engine services.}
      \end{cvitems}
    }
\end{cventries}