\cvsection{Projects}
\begin{cventries}
  \cventry
    {Run on MXNet in Python}
    {Curiosity-LSTM}
    {}
    {Apr. 2017 - NOW}
    {
      \begin{cvitems}
        \item {Define the item novelty criteria and reconstruct LSTM to fit novelty, then implement the model.}
      \end{cvitems}
    }
  \cventry
    {Run on MXNet in Python}
    {Deep Audio-based Music Recommendation}
    {}
    {Jul. 2016 - Jul. 2017}
    {
      \begin{cvitems}
        \item {Collect MSD, EchoNest Taste Profile, and 7Digital Audio Clips Datasets.}
        \item {Use a CNN(4 ConvLayer+ReLU+Maxpooling + 3 FullConnectedLayer) to extraction frame-level features of audio signals.}
        \item {Improve the accuracy of the music recommendation by positioning target songs in collaborative filtering latent space.}
      \end{cvitems}
    }
  \cventry
    {Written in Python}
    {Sogou Persona Prediction : CCF DataFoundation Competition}
    {}
    {Nov. 2016}
    {
      \begin{cvitems}
        \item {Applying LDA to each user's query list to draw topic features, then use SVM and LSTM network to produce the predictions.}
      \end{cvitems}
    }
  \cventry
    {Written in Java}
    {UIS: A novel Social Network User Recommendation framework}
    {}
    {Oct. 2015 - Oct. 2016}
    {
      \begin{cvitems}
        \item {Implement our improved LDA model(combine LDA and GPU) and do parameters tuning.}
        \item {Summarise experimental results and write the thesis.}
      \end{cvitems}
    }
  \cventry
    {Python for data crawling, mongoDB for storage, Lucene for query}
    {Gitsoo: An academic vertical searching engine}
    {}
    {Dec. 2015 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Responsible for the search, sorting algorithm development and data indexing.}
        \item {Responsible for the development of data crawling, MongoDB data storage, and backend Lucene search engine services.}
      \end{cvitems}
    }
\end{cventries}